Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-19 appendix-EPQ.tex
modify

\FiveEnmuerationisEnoughForEPQOneEqual*

>>>>

\begin{restatable}{lemma}{FiveEnmuerationisEnoughForEPQOneEqual}
\label{lemma:five enumeration is enough for EPQ1Equal}
Given a data-differentiated $\textit{pri}$-execution $e$ with $\textit{last}(e) = \textit{EPQ}_1^{=}$. Let $a$ and $b$ be items with maximal priority $\textit{pri}$. Assume that $a <_{\textit{pb}}^* b$, and the rightmost gap-point of $b$ is before $\textit{cal}(\textit{put},a,\textit{pri})$ or $\textit{cal}(\textit{rm},a)$. Then, there are five possible enumeration of method events of $a$, $b$, $a_1$ (if exists), where $a_1$ is the possible intermediate items for obtain $a <_{\textit{pb}}^* b$.
\end{restatable}
\begin {proof}
